Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
add results to spat p

<!-- spatial -->
Habitat selection, the use of available resources or landscape features by
animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009].
Social structure and habitat selection are intimately related and individuals
must share space to interact [@Webber_2018]. Johnson (1980) identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Scales of habitat selection could be
relevant for multilayer networks and our integration of habitat within a
multilayer context could be an important first step (see Figure
\@ref(fig:lcres)). Specifically, if individuals select habitats at the home
range scale, it may be relevant to assess social structure at the home range
overlap scale in a multilayer framework. By contrast, in cases where individuals
select habitats at the patch-scale, more fine-scale measures of sociality may be
relevant. Moving past this hierarchical perspective, Mayor et al. [-@Mayor_2007]
emphasized the importance of considering a broad continuum of scales to reveal
scale-dependent selection and avoid the bias of predefined scales assumed to be
associated with certain behaviours.

<!-- TODO: missing results

As spatial resolution increased, edge overlap
remained stable in open and forest layers but decreased in foraging layers
(Figure \@ref(fig:lcres) D). Graph strength did not change in forest layers
with increasing spatial resolution (Figure \@ref(fig:lcres) E). Foraging and
open layer had greater individual variation in graph strength, and foraging
layers showed an increase in graph strength with increasing spatial resolution
(Figure \@ref(fig:lcres) E). Foraging habitat is rare (12.8% of the landscape)
on Fogo Island and the proportion of relocations in foraging habitat decreased
as spatial resolution increased (14.5% at 30 m - <2% at 1000 m). Despite this,
the foraging layer had similar edge overlap as the open layer at 30 m resolution 
indicating its importance in caribou sociality. 
-->

<!-- spatial -->

@@

We show that multilayer social networks are (1) scale-dependent, and (2) useful
for identifying spatially or temporally specific social associations. When
employing multilayer networks, it is important to consider a broad continuum of
social, spatial and temporal scales to fully capture ecological processes and
establish a clear link between biologically relevant scales of observation.
<!-- conclusion -->

>>>>

<!-- spatial -->
Habitat selection, the use of available resources or landscape features by
animals [@Manly_1993; @Boyce_1999], is a scale-dependent process [@Mayor_2009].
Social structure and habitat selection are intimately related and individuals
must share space to interact [@Webber_2018].

We found edge overlap was stable in open and forest layers but decreasing in 
foraging layers with increasing spatial scale (Figure \@ref(fig:lcres) D).
Graph strength had greater individual variation in open and foraging layers than
in forest layers (Figure \@ref(fig:lcres) E). We observed a decrease in 
the proportion of relocations in foraging habitat with increasing spatial
resolution (14.5% at 30 m - <2% at 1000 m). As the foraging layer  
had similar edge overlap and graph strength as the open layer at 30 m spatial 
resolution despite having lower abundance on the landscape (foraging: 12.8%, 
open: 36.9%), this result highlights the importance of considering
spatial scale when including habitat in multilayer networks. Johnson 
[-@Johson_1980] identified four
orders of habitat selection: (1) the geographical range of a species, (2) the
home range of an individual, the (3) habitat patches within the home range and
(4) specific resources within a habitat patch. Kie et al. [-@Kie_2002] found
that, independently, third order of selection was insufficient for capturing
landscape attributes selected for by mule deer (*Odocoileus hemionus*), at a
scale larger than their home range size. Scales of habitat selection could be
relevant for multilayer networks and our integration of habitat within a
multilayer context could be an important first step (see Figure
\@ref(fig:lcres)). Specifically, if individuals select habitats at the home
range scale, it may be relevant to assess social structure using home
range overlap. By contrast, in cases where individuals
select habitats at the patch-scale, fine-scale measures of sociality may be more
relevant. Moving past this hierarchical perspective, Mayor et al. [-@Mayor_2007]
emphasized the importance of considering a broad continuum of scales to reveal
scale-dependent selection and avoid the bias of predefined scales assumed to be
associated with certain behaviours.
<!-- spatial -->

@@

We show that multilayer social networks are (1) scale-dependent, and (2) useful
for identifying spatially or temporally specific social associations. When
employing multilayer networks, it is critical to consider a broad continuum of
social, spatial and temporal scales to fully capture ecological processes and to
establish a clear link between biologically relevant scales of observation.
<!-- conclusion -->
